pema application

### 2023-02-23 paper/manuscript.Rmd
update paper

authornote: |
  This is a preprint paper, generated from Git Commit # `r substr(gert::git_commit_id(),1,7)`. This work was funded by a NWO Veni Grant (NWO Grant Number VI.Veni.191G.090), awarded to the lead author.

>>>>

authornote: |
  This is the peer reviewed version of the following article: [Van Lissa, C. J., van Erp, S., & Clapper, E. B. (2023). Selecting relevant moderators with Bayesian regularized meta‐regression. Research Synthesis Methods. DOI:10.1002/jrsm.1628]. This paper was generated from Git Commit # `r substr(gert::git_commit_id(),1,7)`. This work was funded by a NWO Veni Grant (NWO Grant Number VI.Veni.191G.090), awarded to the lead author.
